\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-16 Paper/paper.tex
Product edits

We decided to install everything globally because it made writing our scripts easier, but it's not a requirement. Everything can be done with locally installed node modules, instead of using the command by itself the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH\_TO\_REPO/node\_modules/MODULE\_NAME/bin/MODULE\_NAME} or something similar.

>>>>

We decided to install everything globally because it made writing our scripts easier, but it's not a requirement. Everything can be done with locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH\_TO\_REPO/node\_modules/MODULE\_NAME/bin/MODULE\_NAME} or something similar.
